Figure 4 - Motifs

### 2024-07-15 ms_figure_4_motifs.Rmd
move heatmap title from columns to rows

plot_grid(ZnII2Cys6_kmer_1)
```

@@

# ... generate main heatmap with annotations
hm_3mers <- Heatmap(enr_3mers, name = "Pearson's resid.",
                    col = circlize::colorRamp2(
                        breaks = c(-mx, seq(-qs, qs, length.out = 62), mx),
                        colors = colorRampPalette(enrichment_heatmap_colors)(64)),
                    cluster_rows = TRUE, show_row_dend = FALSE,
                    column_dend_reorder = match(colnames(enr_3mers),
                                                c("GCG", "CCG", "GGC", "GGG"),
                                                nomatch = 100),
                    cluster_columns = TRUE, column_dend_height = unit(10, "mm"),
                    row_names_gp = gpar(fontsize = fl, fontfamily = "sans"),
                    column_names_gp = gpar(fontsize = fs, fontfamily = "mono"),
                    column_title = "Binuclear zinc cluster TFs",
                    column_title_side = "top", column_title_gp = gpar(fontsize = ft),
                    border = TRUE, border_gp = gpar(lwd = 0.5),
                    show_row_names = TRUE, show_column_names = TRUE,
                    use_raster = FALSE, show_heatmap_legend = TRUE,
                    bottom_annotation = kmer_annot,
                    heatmap_legend_param = list(at = round(c(-mx, 0, mx), 1),
                                                labels_gp = gpar(fontsize = fl),
                                                border = "gray10",
                                                legend_direction = "horizontal",
                                                legend_width = unit(25, "mm"),
                                                title = "3-mer enrichment   ",
                                                title_position = "lefttop",
                                                title_gp = gpar(fontsize = fl)),
                    width = unit(130, "mm"), # heatmap body width
                    height = unit(3 * nrow(enr_3mers), "mm"))

@@

cowplot::plot_grid(
    cowplot::plot_grid(
        cowplot::plot_grid(ZnII2Cys6_kmer_1, scale = 0.85),
        hm_ZnII2Cys6_sel_3mers,
        labels = c("A", "B"),
        rel_widths = c(2, 3.2),
        nrow = 1
    ),
    cowplot::plot_grid(
        plotlist = motif_characterization_plots,
        ncol = 1,
        rel_heights = c(rep(1, length(motif_characterization_plots) - 1), 0.4)),
    nrow = 2,
    labels = c("", "C"),
    align = "vh",
    axis = "b",
    rel_heights = c(1.4, 3.2)
)
```

>>>>

print(ZnII2Cys6_kmer_1)
```

@@

# ... generate main heatmap with annotations
hm_3mers <- Heatmap(enr_3mers, name = "Pearson's resid.",
                    col = circlize::colorRamp2(
                        breaks = c(-mx, seq(-qs, qs, length.out = 62), mx),
                        colors = colorRampPalette(enrichment_heatmap_colors)(64)),
                    cluster_rows = TRUE, show_row_dend = FALSE,
                    column_dend_reorder = match(colnames(enr_3mers),
                                                c("GCG", "CCG", "GGC", "GGG"),
                                                nomatch = 100),
                    cluster_columns = TRUE, column_dend_height = unit(10, "mm"),
                    row_names_gp = gpar(fontsize = fl, fontfamily = "sans"),
                    column_names_gp = gpar(fontsize = fs, fontfamily = "mono"),
                    row_title = "Binuclear zinc cluster TFs",
                    row_title_side = "left", column_title_gp = gpar(fontsize = ft),
                    border = TRUE, border_gp = gpar(lwd = 0.5),
                    show_row_names = TRUE, show_column_names = TRUE,
                    use_raster = FALSE, show_heatmap_legend = TRUE,
                    bottom_annotation = kmer_annot,
                    heatmap_legend_param = list(at = round(c(-mx, 0, mx), 1),
                                                labels_gp = gpar(fontsize = fl),
                                                border = "gray10",
                                                legend_direction = "horizontal",
                                                legend_width = unit(25, "mm"),
                                                title = "3-mer enrichment   ",
                                                title_position = "lefttop",
                                                title_gp = gpar(fontsize = fl)),
                    width = unit(130, "mm"), # heatmap body width
                    height = unit(3 * nrow(enr_3mers), "mm"))

@@

cowplot::plot_grid(
    cowplot::plot_grid(
        cowplot::plot_grid(ZnII2Cys6_kmer_1, scale = 0.85),
        hm_ZnII2Cys6_sel_3mers,
        labels = c("A", "B"),
        rel_widths = c(1.9, 3.3),
        nrow = 1
    ),
    cowplot::plot_grid(
        plotlist = motif_characterization_plots,
        ncol = 1,
        rel_heights = c(rep(1, length(motif_characterization_plots) - 1), 0.4)),
    nrow = 2,
    labels = c("", "C"),
    align = "vh",
    axis = "b",
    rel_heights = c(1.4, 3.2)
)
```
